\documentclass[times, a4paper, 12pt, onecolumn, oneside]{article} 

\usepackage[a4paper,left=2.0cm,right=2.0cm,bottom=1.0cm,top=2.0cm,includefoot,includehead]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{graphicx} 

\usepackage{fancyhdr}
\pagestyle{fancyplain}
\date{}
\lhead{{\em Surname  (LUT) }}
\chead{Project name}
\rhead{\today}

\usepackage{natbib}
\bibliographystyle{apalike}


\title{Write Your Title}
\author{Your Name}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
    Short abstract, max 100 words. Remember, max 4 page report, including references!
\end{abstract}

\section{Introduction}
\begin{itemize}
    \item Problem statement
    \item Literature / References 
    \item Remember proper citations, for example,  use either \citet{Lindgren2011} or \citep{Roininen2014} -- whenever appropriate. Ask the lecturer or teaching assistants for help, if you need help in citing. 
\end{itemize}


\section{Model}

\begin{itemize}
    \item Give ODE, SDE, similar in Equation form, e.g. 
    \begin{equation} \label{eqn:stochasticprocess}
        X(t) \sim \mathcal N (0,C(t,t')),
    \end{equation}
    where $X(t)$ is the unknown, with $t\in\mathbb{R}$, and it is a zero mean stochastic process with covariance $C(t,t')$.
    \item Clearly explain the target unknown, define all the objects, and the space the objects are in. If needed, refer to Equation \eqref{eqn:stochasticprocess}, if needed (capitalise E).
    \item Write prior, likelihood and posterior distributions.
\end{itemize}

\section{Methods}

\begin{itemize}
    \item Shortly describe the method you are using MCMC/Kalman filter etc.
    \item Which package do you use (Stan/GPStuff/\dots)
\end{itemize}

\section{Numerical Examples}

\begin{itemize}
    \item Make visualisations, use big enough fonts (about the same size as text itself).
    \item Include captions.
    \item Use vector graphics (if possible).
    \item Explain all the figures in the text.
    \item Write: "In Figure XX..." (capitalise F)
\end{itemize}

\section{Conclusions}

\begin{itemize}
    \item Report on usability of the chosen package, e.g.\ Stan with respect to ease of installing, using etc.
    \item The results obtained
    \item Possible future studies, e.g.\ possibility to use in practical engineering or thesis work.
\end{itemize}

\bibliography{references}

\end{document}
